\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{geometry}
\usepackage{afterpage}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{array}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{dcolumn}
\usepackage[strict]{changepage}
\usepackage{etoolbox}
\usepackage{float}
\usepackage{ifthen}
\usepackage{pdflscape}
%\usepackage{lscape}
\usepackage{longtable}
\usepackage[colorlinks]{hyperref}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[sort]{natbib}
\usepackage{pgffor}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{subfig}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{url}
\usepackage{verbatim}
\usepackage{xr}
\usepackage{longtable}
\usepackage{rotating}
\usepackage{color}
\usepackage{tikz}
\usepackage{lscape}

\newcommand{\iid}{\stackrel{\mathrm{i.i.d.}}{\sim}}

\makeatletter
  \newcommand\regsz{\@setfontsize\regsz{12pt}{6}}
\makeatother

\makeatletter
  \newcommand\smlsz{\@setfontsize\smlsz{10pt}{6}}
\makeatother

\renewcommand\scriptsize{@setfontsize\scriptsize{5}{7}} 

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

\restylefloat{table}

\newcommand{\tab}{\hspace*{2em}}



\title{\vspace{-20mm}\regsz \textbf{Maryclare Griffin} \\ 
\vspace{0mm} \hline \vspace{-3mm}
\begin{center}
\begin{tabular}{lcr}
\smlsz Postdoctoral Associate & & \\
\smlsz Cornell University & \hspace{40mm} & \smlsz \url{http://maryclare.github.io} \\
\smlsz Center for Applied Mathematics & \hspace{40mm} &  \smlsz (508)-314-1007 \\
\smlsz 657 Rhodes Hall & \hspace{40mm} & \smlsz maryclare@cornell.edu \\
\smlsz Ithaca, NY 14853 & & \\
\end{tabular}
\end{center}}
\author{\vspace{-25mm}}
\date{\vspace{-25mm}}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\section*{\regsz Education}

\begin{itemize} 
	\item[] \textbf{University of Washington,} Seattle, WA \hfill 2013-2018 \\ 
	Ph.D., Statistics \\
	Advisor: Peter Hoff\text{, } Thesis Title: ``Model-Based Penalized Regression'' \vspace{-2mm}
	\item[] \textbf{Duke University,} Durham, NC \hfill 2016-2018 \\
	Visiting Ph.D. Student \vspace{-2mm}
	\item[]  \textbf{University of Chicago,} Chicago, IL \hfill 2008-2012 \\
	B.A., Economics with Honors, Statistics\vspace{-2mm}
\end{itemize}

\section*{\regsz Employment}

\begin{itemize}
	\item[] \textbf{Economics Research Center, University of Chicago}  \hfill 2012-2013 \\
	Research Assistant with Dr. James Heckman \vspace{-2mm}
\end{itemize}

\section*{\regsz Publications}

\begin{itemize}
	\item[]\textbf{Published}\vspace{-2mm}
	\item[] \underline{Griffin M.}, Hoff, P. D. \href{https://arxiv.org/pdf/1703.08620}{``Lasso ANOVA Decompositions for Matrix and Tensor Data.''} \\
	\tab \emph{ Computational Statistics and Data Analysis.} Forthcoming.  \vspace{-2mm}
	\item[] \underline{Griffin M.}, Erosheva E. A., Fredriksen-Goldsen K., Gile K., Handcock M. (2018) \href{https://projecteuclid.org/euclid.aoas/1542078044}{``A simulation-based framework for assessing the feasibility of respondent-driven sampling for estimating characteristics in populations of lesbian, gay and bisexual older adults.''} \\
	\tab \emph{ Annals of Applied Statistics.} 12(4):2252-2278.  \vspace{-2mm}
	\item[] Holstein, C., \underline{Griffin M.}, Hong J., Sampson P. (2015) \href{https://pubs.acs.org/doi/abs/10.1021/acs.analchem.5b02082}{``A Statistical Method for Determining and Comparing Limits of Detection of Bioassays.''} \\
	\tab \emph{Analytical Chemistry.} 87(19):9795-9801.\vspace{-2mm}
	\item[] \textbf{Preprints} \vspace{-2mm}
	\item[] \underline{Griffin M.}, Hoff, P. D. \href{https://arxiv.org/abs/1712.06230}{``Testing Sparsity-Inducing Penalties.''} \\ 
	\tab \emph{Submitted.} \vspace{-2mm} 
	\item[] \underline{Griffin M.}, Hoff, P. D. \href{https://arxiv.org/pdf/1902.05106.pdf}{``Structured Shrinkage Priors.''} \\
	\tab \emph{In preparation for submission.} \vspace{-2mm}
	\item[] \textbf{Published Software} \vspace{-2mm}
	\item[] \underline{Griffin M.} \href{https://cran.r-project.org/web/packages/gnorm/index.html}{\texttt{gnorm}}: Generalized Normal/Exponential Power Distribution for \texttt{R},  version 1.0.0.  \\
	 \vspace{-2mm}
\end{itemize}

\vspace{-8.32mm}
\section*{\regsz Honors and Awards}

\begin{itemize} 
	\item[] National Science Foundation Graduate Research Fellowship  \hfill 2013-2018 	\vspace{-2mm}
	\item[] Frontiers in Forecasting Best Poster Prize \hfill 2018 \vspace{-2mm}
	\item[] Women in Statistics and Data Science Conference Travel Award \hfill 2016 \vspace{-2mm}
	\item[] Survey Research Methods, Government Statistics, and  \vspace{-2mm}
	\item[] Social Statistics Sections Student Paper Award  \hfill 2015  \vspace{-2mm}
	\item[] University of Washington, Blalock Fellowship \hfill 2013 \vspace{-2mm}
	\item[] University of Chicago, Goldberg Award in Economics  \hfill 2012	\vspace{-2mm}				
%	\item[] University of Chicago Foreign Language Acquisition Grant 	\hfill June 2010\vspace{-2mm} 
%	\item[] Dean's List, University of Chicago \hfill 2008-2012			   					      	
\end{itemize}


\section*{\regsz Teaching Experience}

\begin{itemize}
	\item[] \textbf{Department of Statistics, Cornell University} \hfill Spring 2019 \vspace{-2mm}
	\item[] Instructor for STSCI4550/ILRST4550/ORIE5550: Applied Time Series Analysis
	\item[] \textbf{Department of Statistics, University of Washington} \hfill Spring 2016 \vspace{-2mm}
	\item[] Teaching Assistant for CSS\&S564: Bayesian Statistics 
\end{itemize}
\section*{\regsz Presentations}


\begin{itemize}
	\item[] \textbf{Invited Talks} \vspace{-2mm}
	\item[] Testing Sparsity-Inducing Penalties. \\
	\tab \emph{Department of Biostatistics and Computational Biology Departmental Colloquia,}\\ 
	\tab \emph{University of Rochester, Rochester, NY; October 2018.} \vspace{-2mm}
	\item[] Beyond the Bayesian Lasso: A Review of Continuous Shrinkage Priors. \\
	\tab \emph{Joint Statistical Meetings, Vancouver, WA; August 2018.} \vspace{-2mm}
	\item[] \textbf{Topic Contributed Talks} \vspace{-2mm}
	\item[] Model-Based Testing of Sparsity Inducing Penalties. \\
	\tab \emph{Western North American Region of The International Biometric Society Conference.}
	\tab \emph{Santa Fe, NM; June 2017.} \vspace{-2mm}
	\item[] Using Hierarchical Models to Understand P300-Wave--Based Brain-Computer Interface Performance Among Disabled Adults. \\
	\tab \emph{Joint Statistical Meetings, Chicago, IL; August 2016.} \vspace{-2mm}
	\item[] Assessing Feasibility of Respondent-Driven Sampling Using Pilot Data with an Application to Older Lesbian, Gay, and Bisexual Adults. \\
	\tab \emph{Joint Statistical Meetings, Seattle, WA; August 2015.} 
	\item[] \textbf{Poster Presentations}\vspace{-2mm}
	\item[] Pathwise Coordinate Descent for Power Penalized Regression. \\
	\tab \emph{Non-convex Optimization and Deep Learning Workshop.}\\ 
	\tab \emph{Boston, MA, January 2019.} \vspace{-2mm}
	\item[] Testing Sparsity-Inducing Penalties. \\
	\tab \emph{Bridging the Divide, Machine Learning in Medicine Symposium.}\\ 
	\tab \emph{Ithaca, NY, September 2018.} \vspace{-2mm}
	\item[] Testing Sparsity-Inducing Penalties. \\
	\tab \emph{Cornell Day of Statistics.}\\ 
	\tab \emph{Ithaca, NY, September 2018.} \vspace{-2mm}
	\item[] Testing Sparsity-Inducing Penalties. \\
	\tab \emph{Frontiers in Forecasting, Institute for Mathematics and Its Applications.}\\ 
	\tab \emph{Minneapolis, MN, February 2018.} \vspace{-2mm}
	\item[] Sparse, Structured Matrix Estimation via $\ell_1$ Penalization of ANOVA Decomposition. \\
	\tab \emph{Opening Workshop of the 2016-2017 Program on Optimization, SAMSI.}\\ 
	\tab \emph{Research Triangle Park, NC, September 2016.}
\end{itemize}

\section*{\regsz Service and Affiliations}

\begin{itemize} 
	\item[] \textbf{University of Washington}
	StatCom Member \hfill 2016-2018 \\
	Graduate Student Representative \hfill 2014-2015 \\
	Graduate and Professional Student Senate Representative \hfill 2013-2014 
\end{itemize}

\begin{itemize}
	\item[] \textbf{Reviewer}  \\
	\tab Biometrika \\
	\tab Journal of the American Statistical Association, Theory and Methods \\
	\tab Journal of Computational and Graphical Statistics \\ 
	\tab Statistics Surveys\vspace{-2mm}
	\item[] \textbf{Session Chair} \\
	\tab Joint Statistical Meetings, Vancouver, BC; August 2018 \\
	\tab Joint Statistical Meetings, Baltimore, MD; August 2017 \\
	\tab Joint Statistical Meetings, Seattle, WA; August 2015.\vspace{-2mm}
	\item[] \textbf{Member} \\
	\tab American Statistical Association \\
	\tab  Institute of Mathematical Statistics \\
	\tab Caucus for Women in Statistics \\
	\tab  International Biometric Society
\end{itemize}

%\section*{\regsz Skills}
%
%\begin{itemize} 
%	\item[]  \textbf{Advanced:}  Latex, R, Stata\vspace{-2mm}               				
%	\item[]  \textbf{Intermediate:} C++, Mathematica, Matlab/Octave, Python\vspace{-2mm}	
%	\item[]  \textbf{Basic:} SAS\vspace{-2mm}                     	
%\end{itemize}

\end{document}